Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-04-20 cav2017/cav2017.tex
grants
line break

% first the title is needed
\title{Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants} 
\titlerunning{Automated Formal Synthesis of Digital Controllers}

@@

The tool Pessoa~\cite{mazo2010pessoa} synthesizes correct-by-design embedded
control software in a Matlab toolbox.  It is based on the abstraction of a
physical system to an equivalent finite-state machine and on the computation
of reachability properties over the finite-state machine.  Based on this
safety specification, Pessoa can synthesize embedded controller software for
a range of properties.  The embedded controller software can be more
complicated than the state-feedback control we synthesized, and the
properties available cover more detail.
%
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
%
However, Pessoa does not have consider the quantization error introduced by
Digital-to-Analogue/Analogue-to-Digital conversion needed for synthesizing
fixed-point digital controllers.

>>>>

\title{Automated Formal Synthesis of Digital Controllers for State-Space
Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project
280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}}

\titlerunning{Automated Formal Synthesis of Digital Controllers}

@@

The tool Pessoa~\cite{mazo2010pessoa} synthesizes correct-by-design embedded
control software in a Matlab toolbox.  It is based on the abstraction of a
physical system to an equivalent finite-state machine and on the computation
of reachability properties over the finite-state machine.  Based on this
safety specification, \mbox{Pessoa} can synthesize embedded controller
software for a range of properties.  The embedded controller software can be
more complicated than the state-feedback control we synthesized, and the
properties available cover more detail.
%
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
%
However, Pessoa does not have consider the quantization error introduced by
Digital-to-Analogue/Analogue-to-Digital conversion needed for synthesizing
fixed-point digital controllers.
